\section{INTRODUCTION}

In recent years, \textit{Smart Farming} projects have been growing in popularity as a method to solve the challenges that the agriculture sector is facing in the last decades. 
This projects are based around the \acrfullr{iot} domain, in which sensors and actuators are connected and coordinated to obtain data to represent the real world, this data can 
later be processed to make decisions that will make the farmers life easier.

One of the problems that \textit{Smart Farming} deals with is the real-time protection of crops from different risks. This risks can go from natural 
risks such as wild fires, to wild animals trespassing fences to feed on the crops. IoT systems can also be applied to this problems, detecting in real-time 
these situations and obtaining all the information related to these events. 

Considering that the topic requires fast-response times, new technologies such as \acrfullr{mec} in combination with \textit{Cloud Computing} can be applied to 
process the data as closest as possible to the main use case. This Edge solutions can aggregate all the data from the sensors and, with the help of 
algorithms for decision making, calculate the best possible response in the fastest way possible.


Using this technologies, this document presents the design of a system for the risks management in crops of Madrid, Spain. 

These rural areas in the lasts decades have been declining in population. This creates two problems in relation to fire risks:
\begin{enumerate}
    \item The depopulation of land creates areas with higher risk of fires\cite{Yanosolo}, where intentional fires can be created and extend faster due to the heavy amount of fuel.
    \item Farmers now need to be aware of these areas in case a fire appears.
\end{enumerate}

In addition to the above mentioned, the risk of animal intrusion increases\cite{importanciacazaEspana}, as the perimetral limits of this crops is now uncontrolled.

To achieve the objective mentioned above, \acrshort{iot} technologies are be integrated with edge computing to create a fast-response system.
\todo[inline]{Poner información resumida sobre los casos de uso que afronta este sistema}